A Mechanical Formalization of Higher-Ranked Polymorphic Type Inference

### 2019-03-01 sections/conclusion.tex
conclusion: wip

This is the conclusion.

>>>>

In this paper we have provided the first mechanized formalization of type
inference for higher-ranked polymorphism. This contribution is made possible by
a new type inference algorithm for DK's declarative type sytsem that
incorporates several novel mechanisation-friendly ideas. Firstly, we merge the
traditional type context with the recently proposed concept of judgment chains,
to accurately track variable scopes and to easily propagate substitutions.
Secondly, we use continuation-passing style to return types from the
bidirectional synthesis mode to further tasks.
